Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-08-06 response_2.txt

Reviewer A

> *The annotation guidelines are needed to ensure replicability. Add them as
appendix material.

We've added the English guidelines to the github repository associated with the paper, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al. 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).

@@

> *In table 5 these examples include a lot of noise. Can the authors comments
how to decide on the criteria for rejecting something as FS.

There is of course some noise, but based on our analysis the noise is fairly consistent with the precision numbers in our evaluation (i.e. most of the ICWSM examples are good FS, whereas about half of the BNC are). Hopefully including the guidelines helps with this, since we don't feel it's possible to give succinct explanation of how to decide whether something is an FS: though there are several tests discussed in the guidelines, at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e. Wray's definition as given at the beginning of Section 2.

@@

> - In some place, the paper is not an easy read -- I found a few
expressions that were fairly cryptic even for a seasoned reviewer in
NLP, examples include: "the best (i.e., most parsimonious) explanation
for statistical irregularities due to lexical affinity": what does
"parsimonious explanation", "lexical affinity" (S.1), or "explainedness"
of a node (S.3) mean? I would like to see a more formal definition right
where this concepts are introduced.

The word "parsimonious" is used here in its typical, non-technical sense to refer to explanations which cover the data and yet are as simple as possible. It's used in the introduction, and is just intended to give a sense to the reader of what is to come, in terms of the logic of the model. Since its not a term, nor does it pretend to be, we don't think there's a problem here.

We have excised the term "lexical affinity", which was intended to point at the predictability that remains after syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.

"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition later (Section 3.3). An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked. There's a certain amount of interconnectedness here that makes it impossible to fully satisfy the need to define everything formally up front.

@@

"Cherry-picking" suggests we are just picking the best values for our test set, which is certainly not the case. All of the hyperparameters you mention were in fact subject to some early evaluation on development data and then fixed from that point on. We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is a form of supervision. We picked reasonable values, saw that they worked using a small amount of development data, and moved on. We've removed the reference to [3 ,6] since it seems to have lead to this misinterpretation: we did some post hoc evaluation of what values of C caused the model performance to drop drastically, but that was unrelated to the selection of 4 as our C value, which happened very early in development.

>- Section 3.4: why not looking also at other node visiting strategies?
> E.g., random?

We did test a few options on dev data (based on n-gram length and LPR; not random, though, because we wanted to preserve the deterministic nautre of the model), and decided on count-based sorting. However, we don't think this is interesting or important enough to include as a focus in the paper.

>- Section 4: there exists a plethora of datasets for MWE, why not comparing
> with other datasets: how were the dataset chosen? Also, why not using
> corpora for the same language of different sizes (cf. e.g., Riedl and
> Biemann)?

By datasets, do you mean MWE vocabularies? or MWE corpora like the STREUSLE? We're not sure exactly what you mean, since no corpus annotated with MWE could possibly have the quantity of data required to build an unsupervised model like this. In terms of evaluation, the main reason not to use existing MWE datasets is exactly that, we are not doing traditional MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally. Though it is possible to use MWE datasets for FS evaluation -- see Brooke et al. (2015) who derived a test set from STREUSLE (results were entirely consistent with the results using the FS set we also use here) -- it requires some hackiness that we felt was indefensible for our main evaluation. Note we did include a small, targeted evaluation of recall using STREUSLE in the discussion.  We addressed this issue rather thoroughly in the previous reviewer response.

@@

It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which have linguistic diversity and therefore a much more interesting range of FS pheonomena. Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS (or MWE) phenomena across the language as whole.

We in fact do have corpora of very different sizes for English, namely the ICWSM and BNC (which is about a tenth the size). Perhaps you mean taking smaller version of the same corpus and seeing the effect of data size? This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for that smaller corpus.

> - Section 6: When discussing "the time needed to build and optimize the
> lattice" it would be good to add exact run-time figures

### 2017-08-06 tacl.tex
Tim over and out!

\newcommand{\LPR}{\ensuremath{\text{LPR}}}
\newcommand{\minLPR}{\ensuremath{\text{minLPR}}}
\newcommand{\cover}{\ensuremath{\text{cover}}\xspace}
\newcommand{\clear}{\ensuremath{\text{clear}}\xspace}
\newcommand{\overlap}{\ensuremath{\text{overlap}}\xspace}

@@

From a practical perspective, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}. When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones. Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.

@@

The motivation for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}. One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses. Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. Like FS, lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures). Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners. \newcite{Sakaguchi16} demonstrate that improving fluency (closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.

@@

A simple but effective solution which avoids extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(x_t) = \prod_{i \in bl(x_t)}{\min\Big(1,\frac{\minLPR(x_t)}{y_i\cdot\minLPR(x_i)}\Big)}
\end{displaymath}
where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of minLPR and the node interaction functions:
%
\begin{multline}
	\mathit{expl}(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
\end{multline}
\noindent
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes.  All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.

@@

\begin{algorithm}[t!]
	\caption{Optimization algorithm. $X$ is an ordered list of the nodes in the lattice. Nodes (designated by $x$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $Y$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$. Explainedness values are indicated by $e$. rev=relevant, aff=affected, curr=current}
	\label{alg:opt}
	\begin{algorithmic}

@@

We evaluate our approach across three different languages including evaluation sets derived from four different corpora selected for their size and linguistic diversity. In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}. To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus. Lemmatization included removing all inflectional marking from both words and POS tags. For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum of 4 words.

@@

 \end{tabular}
 \caption{Results of FS identification in various test sets: Countrank = ranking with frequency; PMIrank = PMI-based ranking; minLPRrank = ranking with minLPR; LPRseg = the method of Brooke et \al (2015); ``$-$cl'' = no clearing; ``$-$ovr'' = no penalization of overlaps; ``P'' = Precision; ``R'' = Recall; and ``F'' = F-score. Bold is best in a given column. For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test \protect\cite{yeh2000more}.}
	 \label{tab:main}

@@

One striking thing about the non-English FS is how poorly they translate: many good FS in these languages become extremely awkward when translated into English. This is expected of course for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like 
\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} \gl{repeat occurrences of \gap like this} and 
\begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
\gl{first half comparison}. This highlights the potential importance of focusing on FS when learning a language. Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.

@@

For all four corpora, the lattice optimization algorithm converged within 10 iterations.  Although the optimization of the lattice is several orders of magnitude more complex than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtimes of the two methods are comparable. In the BNC, the full lattice method was much faster than LocalMaxs and DP-Seg, though direct runtime comparisons to these methods are of modest value due to differences of both scope and implementation.

@@

The second author has been supported by an Endeavour Research Fellowship
of the Australian Government, and in part by the Croatian Science
Foundation under the project UIP-2014-09-7312. We would also like to thank our Australian, Japanese, and Croatian annotators.

>>>>

\newcommand{\LPR}{\ensuremath{\text{LPR}}}
\newcommand{\minLPR}{\ensuremath{\text{minLPR}}}
\newcommand{\cover}{\ensuremath{\text{cover}}\xspace}
\newcommand{\clear}{\ensuremath{\text{clear}}\xspace}
\newcommand{\overlap}{\ensuremath{\text{overlap}}\xspace}
\newcommand{\expl}{\ensuremath{\text{expl}}\xspace}

@@

From a practical perspective, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}. When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones. Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure applicable to any possible syntactic pattern, which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.

@@

The motivations for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}. One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses. Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. Like FS, lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures). Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners. \newcite{Sakaguchi16} demonstrate that improving fluency (closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.

@@

A simple but effective solution which avoids extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(x_t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(x_t) = \prod_{i \in bl(x_t)}{\min\Big(1,\frac{\minLPR(x_t)}{y_i\cdot\minLPR(x_i)}\Big)}
\end{displaymath}
where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

The objective function maximized by the model is then the explainedness (\expl) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of \minLPR, the node interaction functions, and the FS status $y_i$ of each node in the lattice:
%
\begin{multline}
	\expl(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ 
        \hspace*{2mm} + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
\end{multline}
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes.  All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.

@@

\begin{algorithm}[t!]
	\caption{Optimization algorithm. $X$ is an ordered list of the nodes in the lattice. Nodes (designated by $x$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $Y$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$. Explainedness values are indicated by $e$. $\mathit{rev}$ = relevant, $\mathit{aff}$ = affected, $\mathit{curr}$ = current}
	\label{alg:opt}
	\begin{algorithmic}

@@

We evaluate our approach across three different languages, including evaluation sets derived from four different corpora selected for their size and linguistic diversity. In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}. To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus. Lemmatization included removing all inflectional marking from both words and POS tags. For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum of 4 words.

@@

 \end{tabular}
 \caption{Results of FS identification in various test sets: Countrank = ranking with frequency; PMIrank = PMI-based ranking; minLPRrank = ranking with minLPR; LPRseg = the method of Brooke et \al (2015); ``$-$cl'' = no clearing; ``$-$ovr'' = no penalization of overlaps; ``P'' = Precision; ``R'' = Recall; and ``F'' = F-score. Bold is best in a given column. For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$ (all $p$-values based on the permutation test: \protect\newcite{yeh2000more}).}
	 \label{tab:main}

@@

One striking thing about the non-English FS is how poorly they translate: many good FS in these languages become extremely awkward when translated into English. This is expected, of course, for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like 
\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} \gl{repeat occurrences of \gap like this} and 
\begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
\gl{first half comparison}. This highlights the potential importance of focusing on FS when learning a language. Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.

@@

For all four corpora, the lattice optimization algorithm converged within 10 iterations.  Although the optimization of the lattice is several orders of magnitude more complex than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtimes of the two methods are comparable. In the BNC, the full lattice method was much faster than LocalMaxs and DP-Seg, though direct runtime comparisons to these methods are of modest value due to differences in both scope and implementation.

@@

The second author was supported by an Endeavour Research Fellowship
from the Australian Government, and in part by the Croatian Science
Foundation under project UIP-2014-09-7312. We would also like to thank
our English, Japanese, and Croatian annotators.
